---
title: 'Part 4: Anomaly Detection'
author: "Allan Mutisya"
date: "1/23/2021"
output: html_document
---

```{r}
#  locale workaround
my_locale <- Sys.getlocale("LC_ALL")
Sys.setlocale("LC_ALL", my_locale)
```
# Advertisement

## 1. Defining the question

### a) Specifying the Question
performing various unsupervised learning techniques and later providing recommendations based on your insights to the marketing departent

### b) Defining the Metric for Success

The analysis will be considered a success when the high dimensional data will be reduced to a low dimension data.

### c) Understanding the context

The role of the analysis is to inform the marketing department on the most relevant marketing strategies that will result in the highest no. of sales.

### d) Recording the Experimental Design

1. Defining the research question

2. Data Understanding

3. Data cleaning

4. Modeling

5. Recommendations

### e) Data Relevance

The datasets are large enough to be used for Exploratory Data Analysis, thus promising better outcomes.

### f) Reading the Data

```{r}
# loading the dataset
library(readr)
sa <- read_csv("C:/Users/ALLANOOH/Documents/moringa/R/IP's/Carrefour/Supermarket_Sales_Forecasting - Sales.csv")

```



```{r}
# Load tidyverse and anomalize
# ---
# 
library(tidyverse)
library(anomalize)
```


```{r}
# previewing the dataset
head(sa)
```

### 3 Data Cleaning
```{r}
# dropping the null values
sup_2 <- drop_na(sa)
sum(is.na(sip_2))
```

```{r}
#  groupby
su <- sup_2 %>% group_by(Date)
str(su)
head(su)
```


### 4. Modeling
```{r}
## STL Decomposition Method

sa %>%
    head(10) %>%
    knitr::kable()
p1 <- sup %>%
    time_decompose(Sales, 
                   method    = "stl",
                   frequency = "1 week",
                   trend     = "3 months") %>%
    anomalize(remainder) %>%
    plot_anomaly_decomposition() +
    ggtitle("# STL Decomposition Method")
p1
```


```{r}
# Twitter Decomposition Method
p2 <- sa %>%
    time_decompose(Sales, 
                   method    = "twitter",
                   frequency = "1 week",
                   trend     = "3 months") %>%
    anomalize(remainder) %>%
    plot_anomaly_decomposition() +
    ggtitle("Twitter Decomposition")
p2
```



We can see that the season components for both STL and Twitter decomposition are exactly the same

### Recommendations

The marketing team should have a great look on the months with the red dots our data





















































































