---
title: 'Part 1: Dimensionality Reduction'
author: "Allan Mutisya"
date: "1/21/2021"
output: html_document
---

```{r}
#  locale workaround
my_locale <- Sys.getlocale("LC_ALL")
Sys.setlocale("LC_ALL", my_locale)
```
# Advertisement

## 1. Defining the question

### a) Specifying the Question
performing various unsupervised learning techniques and later providing recommendations based on your insights to the marketing departent

### b) Defining the Metric for Success

The analysis will be considered a success when the high dimensional data will be reduced to a low dimension data.

### c) Understanding the context

The role of the analysis is to inform the marketing department on the most relevant marketing strategies that will result in the highest no. of sales.

### d) Recording the Experimental Design

1. Defining the research question

2. Data Understanding

3. Data cleaning

4. Modeling

5. Recommendations

### e) Data Relevance

The datasets are large enough to be used for Exploratory Data Analysis, thus promising better outcomes.

### f) Reading the Data

```{r}
# loading the dataset
library(readr)
supa <- read_csv("C:/Users/ALLANOOH/Documents/moringa/R/IP's/Carrefour/Supermarket_Dataset_1 - Sales Data.csv")
```

```{r}
# pre-viewing the dataset
head(supa)

```



### 2. Data Understanding

```{r}
# checking for the structure of the dataset
str(supa)
```



The dataset is comprised of numeric and character data types



### 3. Data cleaning

```{r}
# renaming columns to remove in-between spaces
names(supa)[names(supa) == "Invoice ID"] <- "Invoice_ID"
names(supa)[names(supa) == "Customer type"] <- "Customer_type"
names(supa)[names(supa) == "Product line"] <- "Product_line"
names(supa)[names(supa) == "Unit price"] <- "Unit_price"
names(supa)[names(supa) == "gross margin percentage"] <- "gross_margin_percentage"
head(supa)
```

```{r}
# dropping invoice id and branch columns since they are irrelevant in our analysis
supa_1 <- subset(supa, select = -c(Invoice_ID, Branch, Date, Time))
head(supa_1)
```



```{r}
# label encoding the cartegorical variables

df<- supa_1

head(df)

df$Customer_type  <- factor(df$Customer_type)

df$Gender <- factor(df$Gender)

df$Product_line <- factor((df$Product_line))

df$Payment <- factor(df$Payment)

vec <- sapply(df, is.factor)

catlevels <- sapply(df[vec], levels)

#store the levels for each category
#level appearing first is coded as 1, second as 2 so on

df <- sapply(df, as.numeric)

class(df) #matrix

df <- data.frame(df) 

#converting back to dataframe

head(df)

```


### 4 Modeling

#### T-NSE

```{r}
# Loading our tnse library
library(Rtsne)
```


```{r}
# Curating the database for analysis 
# 
Labels<- df$Total
df$Total<-as.factor(df$Total)

# For plotting
#
colors = rainbow(length(unique(df$Total)))
names(colors) = unique(df$Total)


```



```{r}
## Split IR into two objects: 1) containing measurements 2) containing class type
supa_data <- subset(df, select = -c(Total)) # We are sub-setting to drop the total column
supa_class <- df$Total # getting the class column

## Load the t-SNE library
library(Rtsne)

## Run the t-SNE algorithm and store the results into an object called tsne_results
tsne_results <- Rtsne(supa_data, perplexity=30, verbose=TRUE, max_iter = 500, check_duplicates = FALSE) # You can change the value of perplexity and see how the plot changes

## Generate the t_SNE plot
par(mfrow=c(1,2)) # To plot two images side-by-side
plot(tsne_results$Y, col = "blue", pch = 19, cex = 1.5) # Plotting the first image
plot(tsne_results$Y, col = "black", bg= supa_class, pch = 21, cex = 1.5) # Second plot: Color the plot by the real total type (bg= supa_class)

```



#### Principal Component Analysis

```{r}
pr <- subset(df, select = -c(Total))

supa.pca <- prcomp(pr, cor = FALSE, scores = TRUE)
summary(supa.pca)
```



```{r}
library(factoextra)

fviz_eig(supa.pca)
```



### Recommendations

  According to PCA a maximum of two components are good enough for modeling





